\documentclass[12pt]{letter}
\usepackage{hyperref}
\address{Mariano Forti \\
         ICAMS, Ruhr-Universit\"at Bochum \\
         44801 Bochum, Germany \\
         \texttt{mariano.forti@rub.de}}
\signature{Mariano Forti}
\date{\today}

\begin{document}

\begin{letter}{Editor \\
               Physical Review B \\
               American Physical Society}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled ``Data-efficient machine-learning of complex Fe--Mo intermetallics using domain knowledge of chemistry and crystallography'' for consideration as a Regular Article in Physical Review B.

Topologically close-packed (TCP) phases are critical precipitates in high-performance alloys, yet their large unit cells make exhaustive first-principles screening prohibitively expensive. In this work, we demonstrate that machine-learning models trained on only 262 DFT calculations of simple TCP phases can accurately predict the formation energies of complex TCP phases (R, M, P, $\delta$)---provided the feature representation is informed by domain knowledge of chemistry and crystallography. We introduce coordination-number-resolved averaging (CNAV), a crystallography-aware feature aggregation scheme, and compare three families of local structural descriptors (BOP, ACE, SOAP). Our best models achieve validation RMSE values of 35--42~meV/atom for complex phases, and the predicted energies yield R-phase sublattice occupancies in quantitative agreement with experimental XRD data.

We believe this work is well-suited for Physical Review B because it addresses a fundamental challenge in condensed matter physics: the interplay between structural complexity, bonding, and phase stability in transition-metal intermetallics. The paper combines electronic-structure theory (DFT, tight-binding BOP), machine learning, and thermodynamic modelling within a unified framework.

We suggest the following expert reviewers:
\begin{itemize}
  \item G\'abor Cs\'anyi (University of Cambridge) --- ML interatomic potentials, SOAP descriptors
  \item Gus Hart (Brigham Young University) --- First-principles thermodynamics, alloy theory
  \item J\"org Neugebauer (Max-Planck-Institut f\"ur Eisenforschung) --- DFT of intermetallics, computational materials science
\end{itemize}

The manuscript has not been published previously and is not under consideration elsewhere. All authors have approved the submission.

\closing{Sincerely,}

Mariano Forti \\
on behalf of all authors

\end{letter}

\end{document}
