% Discussion section

\subsection{Why does the simple-to-complex transfer work?}

The success of this approach rests on three pillars. First, the local bonding environments in complex TCP phases are built from the same motifs as those in simple TCP phases: tetrahedrally close-packed coordination polyhedra around sites with CN 12, 14, 15, and 16~\cite{joubert_tcp}. Second, the CNAV feature representation explicitly preserves this crystallographic information by treating different CN environments separately. Third, BOP descriptors---derived from a physically motivated tight-binding model---capture the essential chemistry of $d$-band filling and hybridisation that governs the relative stability of TCP phases~\cite{bopfox, drautz_bop}.

\subsection{Comparison with alternative methods}

Direct DFT calculation of all relevant R-, M-, P-, and $\delta$-phase configurations at every composition would require thousands of calculations. Our approach achieves useful accuracy with fewer than 300 training calculations---a reduction of approximately an order of magnitude. Alternative ML strategies that use only generic composition-based descriptors (e.g., Magpie features~\cite{magpie}) or structure-agnostic fingerprints struggle to capture the subtle energy differences between competing TCP polymorphs (Table~\ref{tab:test_performance}, ``Dataset'' row), underscoring the value of crystallographic domain knowledge.

\subsection{Descriptors for regression vs.\ fitted machine-learning interatomic potentials}

A natural question is whether the BOP advantage would survive against a modern machine-learning interatomic potential (MLIP) --- linear ACE via \texttt{pacemaker}~\cite{pacemaker}, nonlinear GRACE via \texttt{tensorpotential}~\cite{grace}, or message-passing models such as MACE~\cite{mace} --- trained on the same 262-structure simple-TCP set. We deliberately chose a descriptors-plus-regression architecture for three reasons: (i) the target property --- formation energy at the EOS minimum --- is a per-structure scalar, for which a full energy--force--stress potential is sample-inefficient compared with direct scalar regression; (ii) CNAV aggregation imposes crystallographic priors (CN binning, sublattice-aware averaging) that are awkward to encode inside a local MLIP; and (iii) BOP moments inherit physical interpretability from the underlying tight-binding $d$-band picture, connecting descriptor importance to chemical bonding~\cite{hammerschmidt_2008,hammerschmidt_2013}. A fitted MLIP would in principle also deliver forces, phonons, and finite-temperature MD. \emph{A priori}, a well-tuned linear-ACE potential should match or exceed the BOP ensemble on test-set RMSE when forces and stresses are available; the BOP advantage, if it survives, would be most evident in the simple-$\to$-complex transfer regime where physical priors matter most. This benchmark could not be performed here because the raw VASP OUTCAR forces and stresses are no longer available for the 262-structure training set; the Zenodo deposit carries only EOS-minimum energies and relaxed positions~\cite{zenodo}. We identify a head-to-head against a fitted linear-ACE potential as the priority follow-up.

\subsection{Validation-set leakage and test-set optimism}

We highlight a methodological caveat that affects the Table~\ref{tab:test_performance} point estimates: the recursive feature eliminator (\texttt{RFECV}) was applied with 5-fold CV over the full 262-structure dataset, meaning the 53-structure held-out test set was visible to the feature selector. The Table~\ref{tab:test_performance} test RMSEs are therefore \emph{optimistic} estimates. The independent 70-structure complex-TCP validation set (R, M, P, $\delta$; Table~\ref{tab:validation_rmse}) was not used in any fitting or selection step and provides the only fully decoupled assessment of generalisation. We note also that the validation set shares Frank--Kasper coordination polyhedra (CN~12, 14, 15, 16) with the training set by design --- this is precisely what CNAV is meant to exploit --- so a quantitative out-of-domain distance analysis~\cite{janet_kulik_2017,sutton_2020} would be the appropriate follow-up to characterise how ``far'' the complex TCP phases lie from the training manifold.

\subsection{Generality and limitations}
\label{sec:limitations}

The methodology is in principle transferable to other transition-metal binaries that host Frank--Kasper phases, but we have not tested this. A systematic transfer benchmark on Fe--W, Co--Mo, and Ni--Cr--Mo using existing DFT databases~\cite{crivello_tcp,joubert_2008} is left as future work; the Conclusions claim about ``multi-principal element alloys'' has been softened accordingly. Limitations of the present study include: (i) accuracy degrades for configurations near the convex hull where multiple polymorphs are nearly degenerate; (ii) non-magnetic reference states were enforced for all calculations --- magnetic contributions would need to be revisited for Fe-rich compositions beyond the range studied here; (iii) the R-phase sublattice-occupancy comparison was performed at $T = 1700$~K, above the assessed R-phase stability bound; recomputing at the experimental annealing temperature (1473~K) is required for a strict equilibrium comparison; and (iv) the raw DFT OUTCAR archives are no longer available, blocking a direct MLIP benchmark and re-bootstrapping of the reported RMSE values.

\subsection{Data efficiency and CALPHAD implications}

Our results demonstrate a general principle: when training data is scarce, domain knowledge --- here encoded via CNAV and BOP moments derived from tight-binding theory --- is not merely helpful, it is essential. The factor-of-ten reduction in required DFT calculations opens the door to ML-driven exploration of TCP stability in multi-component alloys. A practical deliverable from this work is a set of ML-predicted CEF end-member energies for the R, M, P, and $\delta$ phases (Supplementary Table~S5), provided in a format ready for ingestion into CALPHAD databases~\cite{lukas_calphad}. These complement the CALPHAD assessments of Joubert and Dupin~\cite{joubert_dupin_2004} and Houserová \emph{et al.}~\cite{houserova_2002} by extending the end-member coverage to the structurally complex phases.
